Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-14 summary.Rmd
can now be compiled without R

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, 
                      warning = FALSE, 
                      message = FALSE, 
                      fig.pos = 'H', 
                      fig.align = 'center', 
                      fig.height = 3, 
                      fig.width = 5, 
                      fig.dpi = 300)

@@

Comparing against the ground truth species labels, Algorithm 2 achieves an 
accuracy of 63\% and an adjusted Rand index of `r ari`\%. In comparison, 
\citet{noroozi2019estimation} achieved an adjusted Rand index of 73\% using 
sparse subspace clustering on the same dataset.

@@

In the second example, we applied Algorithm 2 to the British MPs Twitter 
network \cite{greene2013producing}. The original data consists of 419 vertices, 
each corresponding to a British MP belonging to one of five political parties. 
For this data analysis, we subsetted the data as described by 
\citet{307cbeb9b1be48299388437423d94bf1} for their analysis of the same 
dataset, resulting in 329 vertices and two parties ($n = 329, K = 2$). 
\citet{307cbeb9b1be48299388437423d94bf1} were able to obtain a classification 
accuracy of `r round(328 / 329 * 100, 1)`\% via modularity maximization. 
Algorithm 2 obtained a lower 
classification accuracy of `r round(clust.acc * 100, 1)`\%. We can also note 
that Algorithm 2 had a much shorter runtime than modularity maximization.

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      # eval = FALSE,
                      comment = NA, 
                      warning = FALSE, 
                      message = FALSE, 
                      fig.pos = 'H', 
                      fig.align = 'center', 
                      fig.height = 3, 
                      fig.width = 5, 
                      fig.dpi = 300)

@@

Comparing against the ground truth species labels, Algorithm 2 achieves an 
accuracy of 63\% and an adjusted Rand index of 73\%. In comparison, 
\citet{noroozi2019estimation} achieved an adjusted Rand index of 73\% using 
sparse subspace clustering on the same dataset.

@@

In the second example, we applied Algorithm 2 to the British MPs Twitter 
network \cite{greene2013producing}. The original data consists of 419 vertices, 
each corresponding to a British MP belonging to one of five political parties. 
For this data analysis, we subsetted the data as described by 
\citet{307cbeb9b1be48299388437423d94bf1} for their analysis of the same 
dataset, resulting in 329 vertices and two parties ($n = 329, K = 2$). 
\citet{307cbeb9b1be48299388437423d94bf1} were able to obtain a classification 
accuracy of `r round(328 / 329 * 100, 1)`\% via modularity maximization. 
Algorithm 2 obtained a lower 
classification accuracy of 99.1\%. We can also note 
that Algorithm 2 had a much shorter runtime than modularity maximization.
